\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2022-04-20 authors_responses/conditional_accept/authors_response.tex
Made all small changes from Benjamin's final proof read. Updated diff and response accordingly

We regret that there was some confusion about the prediction step of the presented localisation algorithm. Equations $26$-$27$ are the EKF (EIF) update equations (rather than the prediction equations), resulting in updated terms $\vec{y}_{k|k}$ and $\mat{Y}_{k|k}$ from the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$. The Gaussian assumption has indeed been removed from the system model, and obtaining the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$ can be computed using any local filter (linearising or otherwise) as mentioned in Section V. The Gaussian assumption that remains is only present in the measurement model, as is a commonly done to simplify the modelling of sensors, and the non-linear distance-measurement function $h_i$ is linearlised by an appropriate EKF filter for the localisation update step only. We hope this clarifies equations $26$-$27$ and the use of the EKF.

>>>>

We regret that there was some confusion about the prediction step of the presented localisation algorithm. Equations $(26)$ -- $(27)$ are the EKF (EIF) update equations (rather than the prediction equations), resulting in updated terms $\vec{y}_{k|k}$ and $\mat{Y}_{k|k}$ from the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$. The Gaussian assumption has indeed been removed from the system model, and obtaining the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$ can be computed using any local filter (linearising or otherwise) as mentioned in Section V. The Gaussian assumption that remains is only present in the measurement model, as is a commonly done to simplify the modelling of sensors, and the non-linear distance-measurement function $h_i$ is linearlised by an appropriate EKF filter for the localisation update step only. We hope this clarifies equations $(26)$ -- $(27)$ and the use of the EKF.
